Energy and the CES production function

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw

  modelsCSP <- list()
  # Output elasticities based on cost share principle
  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
  betaCSP <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    for (adj in c("unadjusted", "adjusted")){
      # Replace with better code later. 
      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
      # or something like that.
      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
      yVar <- as.name(summands(form, n=1, right=FALSE))
      kVar <- as.name(summands(form, n=1))
      lVar <- as.name(summands(form, n=2))
      tVar <- as.name(summands(form, n=3))
      data <- historicalData[[country]]
      formula <- substitute(
        log(Y) - alpha_1 * log(K) - alpha_2 * log(L) ~ T,
        list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
      )
      # Cobb-Douglas
      cdModCSP <- 
        eval(substitute( 
          plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
              optimize = FALSE),
          list(formula = formula)))

>>>>

  modelsCSP <- list()
  # Output elasticities based on cost share principle
  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
  betaCSP <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    for (adj in c("unadjusted", "adjusted")){
      # Replace with better code later. 
      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
      # or something like that.
      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
      yVar <- as.name(summands(form, n=1, right=FALSE))
      kVar <- as.name(summands(form, n=1))
      lVar <- as.name(summands(form, n=2))
      tVar <- as.name(summands(form, n=3))
      data <- historicalData[[country]]
      formula <- substitute(
        log(Y) - (alpha_1 * log(K) + alpha_2 * log(L)) ~ T,
        list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
      )
      # Cobb-Douglas
      cdModCSP <- 
        eval(substitute( 
          plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
              optimize = FALSE),
          list(formula = formula)))
